The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-04-27 paper/main.tex
squeezing paper to fit 14 pages

\author{Ty Trusty}

\email{trusty@cs.toronto.edu}
%
\author{Honglin Chen}

\email{chl9797@cs.toronto.edu}
%
%
\author{David I.W. Levin}
\email{diwlevin@cs.toronto.edu}

\affiliation{%
 \institution{University of Toronto}
 \streetaddress{40 St. George Street}
 \city{Toronto}
 \state{ON}
 \country{Canada}
 \postcode{M5S 2E4}
}

@@

>>>>

\author{Ty Trusty}
\email{trusty@cs.toronto.edu}
\affiliation{%
 \institution{University of Toronto}
 \streetaddress{40 St. George Street}
 \city{Toronto}
 \state{ON}
 \country{Canada}
 \postcode{M5S 2E4}
}
%
\author{Honglin Chen}
\email{chl9797@cs.toronto.edu}
\affiliation{%
 \institution{University of Toronto}
 \streetaddress{40 St. George Street}
 \city{Toronto}
 \state{ON}
 \country{Canada}
 \postcode{M5S 2E4}
}
%
%
\author{David I.W. Levin}
\email{diwlevin@cs.toronto.edu}
\affiliation{%
 \institution{University of Toronto}
 \streetaddress{40 St. George Street}
 \city{Toronto}
 \state{ON}
 \country{Canada}
 \postcode{M5S 2E4}
}

@@

\begin{acks}
This work is funded in part by NSERC Discovery (RGPIN-2017-05524), Connaught Fund (503114), CFI-JELF Fund, Accelerator (RGPAS-2017-507909), and the Canada Research Chairs Program.
We thank Abhishek Madan, Otman Benchekroun, Sarah Kushner, Michael Tao, Nicholas Vining, and Christopher Batty for proofreading; anonymous reviewers for their helpful comments and suggestions.
\end{acks}

### 2021-04-27 paper/sections/results.tex
squeezing paper to fit 14 pages

%editing example
For downstream applications, the output of  SEM simulation is itself editable in a NURBS modelling program (see \reffig{edit}). 
This can be useful for visual effects pipelines, allowing artists to easily post-process animations using the same tools in which they were created.
\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/export_iges.pdf}
  \caption{Here we show the output of an SEM animation loaded into Rhinoceros 3D 7 for additional editing.\ty{note: initial version of figure. Currently remaking it :)}}
  \label{fig:edit}
\end{figure}

@@

\begin{figure*}[htp]
  \includegraphics[width=\textwidth,height=3in]{figures/starship.pdf}
  \caption{Our SEM is robust to stiff materials, complicated geometry and non-trivial collisions. Here we show the Space-V starship makes a graceful landing on the rugged surface of Mars. }
  \label{fig:starship}
\end{figure*}

>>>>

%editing example
For downstream applications, the output of SEM simulation is itself editable in a NURBS modeling program (see \reffig{edit}). 
%This can be useful for visual effects pipelines, allowing artists to easily
% post-process animations using the same tools in which they were created.
This can allow artists to easily post-process animations using the same tools in which they were created.
\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/export_iges.pdf}
  \caption{Here we show the output of an SEM animation loaded into Rhinoceros 3D 7 for additional editing.\ty{note: initial version of figure. Currently remaking it :)}}
  \label{fig:edit}
\end{figure}

@@

\begin{figure*}[htp]
  %\includegraphics[width=\textwidth,height=3in]{figures/starship.pdf}
  \includegraphics[width=\textwidth]{figures/starship_short.pdf}
  \caption{Our SEM is robust to stiff materials, complicated geometry and non-trivial collisions. Here we show the Space-V starship makes a graceful landing on the rugged surface of Mars. }
  \label{fig:starship}
\end{figure*}
